Predicting and Preventing Employee Turnover through HR Analytics

### 2024-07-30 products/manuscript/Manuscript.qmd
final project

---
title: "Predicting and Preventing Employee Turnover through HR Analytics"
subtitle: ""
author: Guillermo Gallardo
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

>>>>

---
title: "Predicting and Preventing Employee Turnover through HR Analytics"
subtitle: ""
author: Guillermo Gallardo
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---
